---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `{shinydataviewer}`

<!-- badges: start -->
<!-- badges: end -->

`shinydataviewer` provides a reusable Shiny module for viewing tabular data
with a searchable table and a variable summary sidebar inspired by the Positron
data viewer.

## Installation

You can install the development version of `{shinydataviewer}` from GitHub:

```{r, eval=FALSE, echo=TRUE}
pak::pak("Ryan-W-Harrison/data-explorer-module")
```

## Package interface

The package is designed to be used as a reusable Shiny module. The main exported
functions are:

- `data_viewer_ui(id)`
- `data_viewer_server(id, data)`
- `data_viewer_card_ui(id, title = NULL)`
- `summarize_columns(df)`

`data` should be a reactive expression that returns a `data.frame`.

## Minimal module example

Use the module directly when you want the explorer layout to manage its own main
table region:

```{r, eval = FALSE}
library(shiny)
library(bslib)
library(shinydataviewer)

ui <- page_fillable(
  theme = bs_theme(version = 5),
  data_viewer_ui("viewer")
)

server <- function(input, output, session) {
  data_viewer_server(
    "viewer",
    data = reactive(iris)
  )
}

shinyApp(ui, server)
```

## Embedded card example

Use `data_viewer_card_ui()` when the viewer needs to live inside a larger
dashboard or reporting layout:

```{r, eval = FALSE}
library(shiny)
library(bslib)
library(shinydataviewer)

ui <- page_fillable(
  theme = bs_theme(version = 5),
  layout_columns(
    col_widths = c(4, 8),
    card(
      card_header("Context"),
      card_body("Supporting content goes here.")
    ),
    card(
      card_header("Dataset"),
      card_body(
        fill = TRUE,
        data_viewer_card_ui("viewer", title = NULL, full_screen = FALSE)
      )
    )
  )
)

server <- function(input, output, session) {
  data_viewer_server(
    "viewer",
    data = reactive(mtcars)
  )
}

shinyApp(ui, server)
```

An additional runnable example is included at
`inst/examples/embedded-card-example.R`.

## Theming and branding

The viewer styles are attached as a package dependency and use Bootstrap 5
theme variables instead of fixed colors. In practice, that means the module will
follow the active `bslib` theme and should pick up branding supplied through
`bs_theme()` or a `brand.yml`-driven theme without additional module-specific
configuration.

```{r, eval = FALSE}
ui <- page_fillable(
  theme = bs_theme(
    version = 5,
    brand = "brand.yml"
  ),
  data_viewer_card_ui("viewer")
)
```

## Data summary helper

If you want access to the same summary data used by the module's variable panel,
you can call `summarize_columns()` directly:

```{r, eval = FALSE}
summarize_columns(iris)
```

## About

You are reading documentation for version `r read.dcf("DESCRIPTION")[1, "Version"]`.
